Clustering time series based on probability distributions across temporal granularities

### 2021-11-18 main.Rmd
something is a bit strange with the scenario 2 and 3 bold text, might still need more fixing

\noindent **Scenario 2 (S2) - Few significant granularities:**
This is the case where one granularity will remain the same across all designs. We consider the case where the distribution of $v$ varies across $g2$ levels for all designs, across $g3$ levels for a few designs, and $g1$ does not vary across designs. The proposed design is shown in Figure \ref{fig:gran2and1-clubbed}(b).

\noindent **Scenario 3 (S3) - Only one significant granularity:**
Only one granularity is responsible for identifying the designs in this case. This is depicted in Figure \ref{fig:gran2and1-clubbed} (right) where only $g3$ affects the designs significantly.

>>>>

**Scenario 2 (S2) - Few significant granularities:**
This is the case where one granularity will remain the same across all designs. We consider the case where the distribution of $v$ varies across $g2$ levels for all designs, across $g3$ levels for a few designs, and $g1$ does not vary across designs. The proposed design is shown in Figure \ref{fig:gran2and1-clubbed}(b).

**Scenario 3 (S3) - Only one significant granularity:**
Only one granularity is responsible for identifying the designs in this case. This is depicted in Figure \ref{fig:gran2and1-clubbed} (right) where only $g3$ affects the designs significantly.
